We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-02 paper/paper.tex
add covariances in text

\begin{table*}
  \centering
  \begin{tabular}{c|c|c|c|c|c|c|}
    \hline
        & M31 & M31 &M31 & MW & MW &MW\\
        & $w$ & $c/a$ & $b/a$ & $w$ & $c/a$ & $b/a$ \\     \hline
M31 $w$ & & & & & & \\ 
M31 $c/a$ & & & & & & \\ 
M31 $b/a$ & & & & & & \\ 
MW $w$ & & & & & & \\ 
MW $c/a$ & & & & & & \\ 
MW $b/a$ & & & & & & \\ 
  \end{tabular}
  \begin{tabular}{c|c|c|c|c|c|c|}
    \hline
        & M31 & M31 &M31 & MW & MW &MW\\
        & $w$ & $c/a$ & $b/a$ & $w$ & $c/a$ & $b/a$ \\     \hline
M31 $w$ & & & & & & \\ 
M31 $c/a$ & & & & & & \\ 
M31 $b/a$ & & & & & & \\ 
MW $w$ & & & & & & \\ 
MW $c/a$ & & & & & & \\ 
MW $b/a$ & & & & & & \\ 
  \end{tabular}

  \caption{Correlation matrix for the normalized values of $w$, $c/a$
    and $b/a$ computed from the $20$ pairs in the Illustris-1
    simulation (left) and the ELVIS project (right).}
\end{table*}

@@

\end{document}

>>>>

@@

Illustris
\begin{verbatim}
[[ 0.8344  0.7849  0.4186 -0.1155  0.0340 -0.1614]
 [ 0.7849  1.1698 -0.1568 -0.0793  0.0362 -0.1213]
 [ 0.4186 -0.1568  0.9606 -0.1151 -0.0150 -0.1098]
 [-0.1155 -0.0793 -0.1151  0.7873  0.6339  0.4006]
 [ 0.0340  0.0362 -0.0150  0.6339  0.6932  0.0652]
 [-0.1614 -0.1213 -0.1098  0.4006  0.0652  0.6100]]
\end{verbatim}

\begin{verbatim}
[-0.1852 -0.4152    -0.2002 -0.1786 -0.4072 -0.2394]
\end{verbatim}

ELVIS
\begin{verbatim}
[[ 1.6051  1.2207  0.7062  0.0833  0.1063  0.0812]
 [ 1.2207  1.0872  0.3584  0.0298  0.1085 -0.0324]
 [ 0.7062  0.3584  0.6363  0.0904  0.0194  0.1601]
 [ 0.0833  0.0298  0.0904  0.4534  0.6138 -0.1159]
 [ 0.1063  0.1085  0.0194  0.6138  1.2120 -0.6372]
 [ 0.0812 -0.0324  0.1601 -0.1159 -0.6372  0.6475]]
\end{verbatim}

\begin{verbatim}
[-0.1803 -0.2829 -0.2205 -0.3292 -0.7484 -0.0863]
\end{verbatim}
\end{document}
